### 2013-07-19 term-paper/paper.tex
Added: paper.tex

\documentclass[12pt]{article}

\usepackage{graphics}
\usepackage{epsfig}
\usepackage{times}
\usepackage{amsmath}
%\usepackage{natbib}
%\usepackage[style=authoryear]{biblatex}
% \addbibresource{mendely.bib} 
% <http://psl.cs.columbia.edu/phdczar/proposal.html>:
%
% The standard departmental thesis proposal format is the following:
%        30 pages
%        12 point type
%        1 inch margins all around = 6.5   inch column
%        (Total:  30 * 6.5   = 195 page-inches)
%
% For letter-size paper: 8.5 in x 11 in
% Latex Origin is 1''/1'', so measurements are relative to this.

\topmargin      0.0in
\headheight     0.0in
\headsep        0.0in
\oddsidemargin  0.0in
\evensidemargin 0.0in
\textheight     9.0in
\textwidth      6.5in

\title{{\bf An Introduction on Recent Advances in Unsupervised Relation Extraction} \\
\it Term Paper for Recent Advances on Semantics \\ supervised by Prof.Dr.Pinkal}
\author{ {\bf Ehsan Khoddammohammadi}  \\
Faculty of Computational Linguistics \\
Saarland University\\
{\small ehsank@coli.uni-saarland.de}
}
\date{\today}

\begin{document}
\pagestyle{plain}
\pagenumbering{roman}
\maketitle

\pagebreak
\begin{abstract}

The aim of this paper is to review recent and influential methods on
Unsupervised Relation Extraction. In the first part, the definition and a general background
for relation extraction task is provided which identifies important aspects and
difficulties of the task. In the second part, five major previous works are
briefly reviewed. An extra section will be dedicated to a weakly supervised method, distant supervision, which is 
necessary due to its impact on recent advances in the task. And
finally in the last part, the paper will be concluded by comparing the discussed methods.

\end{abstract}

\pagebreak
\tableofcontents
\pagebreak

\cleardoublepage
\pagenumbering{arabic}

\section{Introduction}
\label{ch:intro}

This part provides an overall introduction of the unsupervised relation extraction task, including
definition and various formulations of the task.

\subsection{Definition}
\label{ch:intro}

Relation Extraction is the task of detecting and classifying semantic rela-
tionship between named entities (NE). The goal of this task is to find a triple
of binary relations and their arguments. For instance, we want to induce a
relation like \emph{bornIn} with its arguments which could be for example like this:\emph{ (
bornIn, Richard Stallman, New York )}. Applications of such task is numerous
in natural language processing; Question/Answering, machine translation and
text summarization are systems that benefit from relation extraction.

In this task, we are trying to have a model to find paraphrases which means
that we are interested to have all the similar semantically similar relations under
one umbrella. So it is desired to have all different surface realizations of one
relation like \emph{isGivenBirth, isBorn, isFrom} in a same set, namely \emph{bornIn}.

Here, in this paper, we only limit ourselves to review unsupervised relation discovery methods. 
One should mention that there are other approaches for this task based on the extent of resources that they use.
 The different category of approaches is dependent on if they heavily use annotated corpora (supervised learning) or 
 small amount of training data (weakly supervised learning). Here, in contrast, 
 We just discuss methods that do not use annotated resources for inducing the relations and finding the arguments.

\section{Major Recent Works on Unsupervised Relation Extraction}
\label{ch:related}

From a classic method, DIRT, to very famous frameworks ,
TextRunner or distant supervision, and more recent works e.g. PATTY,
all are examples of several different family of approaches. These methods could
be categorized from different perspectives (1) amount of annotated data they
need (2) if they can only handle a predefined enumeration of entities and re-
lations or are open to any number of relations (3) organization of semantic
interpretation and (4) underlying family of methods they use.
he content of your proposal. Each topic occupies one section, each
with their own conclusion and future work.
In this section we will review these major works. We will discuss their formulation of the task, their models
 and the features they incorporate, the model constraints and finally we will take a look at how good a model is performing.

\subsection{DIRT}
\label{ch:unsupervised}

\subsection{TextRunner}
\label{ch:unsupervised}

\subsection{USP}
\label{ch:unsupervised}

\subsection{PATTY}
\label{ch:unsupervised}

\subsection{Rel-LDA \& Type-LDA}
\label{ch:unsupervised}

\section{Weakly Supervised on Relation Extraction Task}
\label{ch:related}

\subsection{Distant Supervision}
\label{ch:weakly supervised}

The content of \cite{Huang2012} your proposal. Each topic occupies one section, each
with their own conclusion and future work.

\section{Conclusion}
\label{ch:conclusion}

\subsection{Analysis}
\label{ch:conclusion}

Based on what we have seen in recent works, we can now give a list of vital
attributes that a state-of-the-art model for extracting relations from open text
should be able to carry out. The author will use these facts to suggest a list of possible improvements
in the next section. Modeling all of
these factors in a joint model is the necessary step to push forward the previous
works.

\begin{description}

  \item[The number of relations and entities is an unknown parameter.] \hfill \\
  The model can not be confined to a limited set of relations or entities. Being able to extract relations in
  open domain text is the first and (most likely) a trivial attribute of the model. More non-trivial feature
  of the model should be its ability to extract as many relations as there are in text. 
  Giving this freedom
  about the model complexity to have no assumption about the exact number of entities and relations
  is suggested by the applicant to be beneficial 
   and is also supported in the literature.
   %\citep{Yates2007}\citep{Mintz2009}

  \item[Relations may not be expressed explicitly in text.] \hfill \\
  Relation extraction task is definitely more than finding paraphrases. The model should be able to handle
  long-distance relations among entities as well as hidden semantic indications of a relation.

  %\citep{PoonDomingos2009}

  \item[Relations and entities have their inner organization and types.] \hfill \\
  It is shown by several recent works that relations of relations play a substantial role in identifying
  relations. Relations and entities belong to a hierarchy of types and therefore the constraints they put on each other
  should be learnt as well.
  %\citep{Yao2011}\citep{Alfonesca2012}\citep{NakasholeWeikum2012}

  \item[Using KB is necessary but not enough.] \hfill \\
  There are more relations among entities than what is collected in 
  Knowledge Bases e.g. Freebase. At the same time, it is statistically shown that a supervision
  from such resources strongly contributes to convergance of any model to a better 
  objective configurations.
  %\citep{Mintz2009}\citep{Bordes2011}\citep{Yao2011}

  \item[Relations and entities are sharing information within each other.] \hfill \\
  Relations and entities should be learnt jointly since they share same explanatory factors (hidden variables)
  . Meaning of a entity can be learnt from its relation to other entities and same argument holds among relations.
  Basically, the model should be able to carry multi-task learning. 
  %\citep{Yao2011}\citep{Bordes2011}

\end{description}

\subsection{Summaru}
\label{ch:conclusion}

Provide an overview of what you have done and what need to be done.

%\subsection{Plan for completion of the research}

%Table \ref{tab:plan} shows my plan for completion of the research.

%\begin{table}[hc]
%\begin{small}
%\begin{center}
%\begin{tabular}{lll}
%Timeline & Work & Progress\\
%\hline
%          & XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX & completed\\
%Nov. xxxx & XXXXXXXXXXXXXXXXXXXXXXXXXXX & ongoing\\
%Jan. xxxx & Thesis writting & \\
%Feb. xxxx & Thesis defense & \\
%\end{tabular}
%\end{center}
%\end{small}
%\caption{Plan for completion of my research}
%\label{tab:plan}
%\end{table}

\pagebreak

\begin{footnotesize}
\bibliographystyle{plain}
%\bibliographystyle{agsm}
\bibliography{mendely.bib}
%\printbibliography
\end{footnotesize}

\end{document}

### 2013-07-19 term-paper/paper.tex
Modified: paper.tex LDA part

@@
-\documentclass[12pt]{article}
+\documentclass[12pt]{report}
 
@@
 
-\begin{document}
+\begin{report}
 \pagestyle{plain}
@@
 
-\section{Introduction}
+\chapter{Introduction}
 \label{ch:intro}
@@
 
-\subsection{Definition}
+\section{Definition}
 \label{ch:intro}
@@
 
-\section{Major Recent Works on Unsupervised Relation Extraction}
+\chapter{Major Recent Works on Unsupervised Relation Extraction}
 \label{ch:related}
@@
 
-\subsection{DIRT}
+\section{DIRT}
 \label{ch:unsupervised}
 
-\subsection{TextRunner}
+\section{TextRunner}
 \label{ch:unsupervised}
 
-\subsection{USP}
+\section{USP}
 \label{ch:unsupervised}
 
-\subsection{PATTY}
+\section{PATTY}
 \label{ch:unsupervised}
 
-\subsection{Rel-LDA \& Type-LDA}
+\section{Rel-LDA \& Type-LDA}
 \label{ch:unsupervised}
 
-\section{Weakly Supervised on Relation Extraction Task}
+In this section we will review the method proposed for relation discovery  by Yao et. al. 
+The method they  proposed is an unsupervised method using generative models which is based on 
+modification of well-known model, Latent Dirichlet Allocation. 
+They have invented three similar models which we will go through them in following. 
+We elaborate on input of the three models and then we describe their generative story 
+and at the end we will finish this part by discussing about  model evaluation.
+
+\subsection{Input format and preprocessing}
+\label{ch:input}
+Authors have chosen a subset of New York Times articles from year 2000 to 2007 which parts with
+abnormal style of writing like obituary content or hard structures to deal like lists are filtered out.
+They have done several pre-processing steps:
+\begin{enumerate}
+\item Tokenization
+\item Sentence split
+\item POS tagging (all last three steps with Stanford tools)
+\item Named entity tagging (Finkel2005)
+\item Dependency parsing (MaltParser)
+\end{enumerate}
+Among all dependency paths we are just interested in those which link two named entities.
+ So basically we are hopeful that realization of one relation is available somewhere in this 
+ path most likely as a verb which relates two mentioned named entities. We collect these kinds of 
+ paths and based on some conditions that we have already discussed in ??? DIRT we filter out non-important links.
+
+ As an example ???
+ Finally in this phase, 2.5 million dependency paths were collected 
+ which will serve as an input to the models that we describe in the next subsection.
+
+\subsection {Model Description}
+\label{ch:model}
+
+\subsection {Evaluation}
+\label{ch:evaluation}
+
+\chapter{Weakly Supervised on Relation Extraction Task}
 \label{ch:related}
 
-\subsection{Distant Supervision}
+\section{Distant Supervision}
 \label{ch:weakly supervised}
@@
 
-\section{Conclusion}
+\chapter{Conclusion}
 \label{ch:conclusion}
 
-\subsection{Analysis}
+\section{Analysis}
 \label{ch:conclusion}
@@
 
-\subsection{Summaru}
+\section{Summaru}
 \label{ch:conclusion}

### 2013-07-19 term-paper/paper.tex
Modified: LDA

@@
 
-\title{{\bf An Introduction on Recent Advances in Unsupervised Relation Extraction} \\
+\title{{\bf A Review on Recent Advances in Unsupervised Relation Extraction} \\
 \it Term Paper for Recent Advances on Semantics \\ supervised by Prof.Dr.Pinkal}
@@
 
-\begin{report}
+\begin{document}
 \pagestyle{plain}
@@
 The aim of this paper is to review recent and influential methods on
-Unsupervised Relation Extraction. In the first part, the definition and a general background
+Unsupervised Relation Extraction. In the first chapter, the definition and a general background
 for relation extraction task is provided which identifies important aspects and
-difficulties of the task. In the second part, five major previous works are
-briefly reviewed. An extra section will be dedicated to a weakly supervised method, distant supervision, which is 
+difficulties of the task. In the second chapter, five major previous works are
+briefly reviewed. The third chapter is dedicated to a weakly supervised method, distant supervision, which is 
 necessary due to its impact on recent advances in the task. And
-finally in the last part, the paper will be concluded by comparing the discussed methods.
+finally in the last chapter, the paper will be concluded by comparison of discussed methods and important lessons learned from each of them.
 
@@
 \label{ch:input}
-Authors have chosen a subset of New York Times articles from year 2000 to 2007 which parts with
-abnormal style of writing like obituary content or hard structures to deal like lists are filtered out.
+Authors have chosen a subset of New York Times articles from year 2000 to 2007 which some of its parts with
+abnormal style of writing like obituary content are filtered out.
 They have done several pre-processing steps:
@@
 \item Sentence split
-\item POS tagging (all last three steps with Stanford tools)
-\item Named entity tagging (Finkel2005)
-\item Dependency parsing (MaltParser)
+\item POS tagging (?? all last three steps with Stanford tools)
+\item Named entity tagging ( ?? Finkel2005)
+\item Dependency parsing (??MaltParser)
 \end{enumerate}
-Among all dependency paths we are just interested in those which link two named entities.
- So basically we are hopeful that realization of one relation is available somewhere in this 
- path most likely as a verb which relates two mentioned named entities. We collect these kinds of 
- paths and based on some conditions that we have already discussed in ??? DIRT we filter out non-important links.
+Among all dependency paths they are just interested in those which link two named entities.
+ Authors assume that realization of one relation is available in this 
+ path most likely as a verb which relates two mentioned named entities. These types of 
+ paths are collected and based on some conditions that we have already discussed in (??? DIRT), non-important links are filtered out.
 
@@
 \label{ch:model}
+All the three models in this work are generative models. Generative models are jointly modeling hidden variables and observable variables and 
+are in contrast to discriminative models. For more information on generative models please see ?? and ??.\\
+
+\textbf{Rel-LDA} is the first model proposed in (?? Yao). 
+In this model, features, $f$, are generated from a distribution , $\Phi_{rf}$. Each type
+ of relation is represented with a binary indicator variable, $r$. Each document is a mixture of few relations
+  and relations are generated from a multinomial distribution $\Theta_{doc}$. $\Theta_{doc}$ is a distribution
+  of relations for a specific document and can be shown as $P(r|doc)$. By choosing a right prior distribution for $\Theta$
+   and $\Phi$ we can impose an assumption that any document contains a few number of relation types. 
+   Another advantage of having prior is that it helps to avoid overfitting. Dirichlet prior with small parameter $\alpha$ is 
+   chosen for this purpose in the paper. For more on the role of priors and specially Dirichlet prior
+    please read ?? and ??.
+    Rel-LDA is decribed with a graphical model in figure ???.
+    Shaded circles are showing the observable variables and other circles are hidden variables except 
+    the priors which are set by ourselves. The direction of arrow shows the dependency in this sense 
+    that destination node (variable) is dependent on source node.
+
+    Features or observable variables in Rel-LDA are:
+    \begin{itemize}
+      \item The dependency path
+      \item Source of the path (the first named entity)
+      \item Destination of the path (the second named entity)
+    \end{itemize}
+
+   	An exact sampling method called \emph{variational inference} is used by authors to compute 
+   	the posterior distribution of the model, $P(r|f)$.
+   	After learning, we will have clusters of relation types which each instance of a specific cluster 
+   	is a relation that is supposed to be semantically equivalent to the other members of this cluster.
+   	\\
+
+   	In the second model, \textbf{Rel1-LDA},The only difference is that  more features are used in the learning procedure.
+   	 The idea is that using more features could be useful as tie-breakers and also discriminators between instances
+   	  to make new clusters. With direct reference to the paper, the authors believe that more features 
+   	  lead to better refinement of clusters. We will see later that this assumption holds in practice.
+   	   The new features that they have introduced in this new model are:
+   	   \begin{itemize}
+   	     \item Trigger: Any word in a dependency path except than stop words. 
+   	     \item Part of speech sequence: The sequence of pos tags of a dependency path. 
+   	     \item Named entity pair: The type of source and destination named entity. 
+   	   \end{itemize}
+
+ Among all the newly introduced features, NE pair is the most interesting one which leads to a 
+ significant observation that the third model will try to address that. Authors observed that 
+ Rel-LDA will put these three relations in one cluster because the second argument of all of them is location:
+
+ \begin{enumerate}
+   \item \emph{ X was born in Y}
+   \item \emph{ X lives in Y}
+   \item \emph{ X, a company in Y}
+ \end{enumerate}
+
+ While the first argument in the first two relations refers to a PER, the first argument of the 
+ third relation is an instance of ORG type. By using NER pairs as feature we can split this cluster 
+ to two clusters with respect to basic types of NE in relations arguments. 
+ This observation leads us to invest more on type identification of arguments to have more pure 
+ clusters and is the main focus of the third model, \textbf{Type-LDA}.
+
+ Selectional preferences of a relation are constraint over possible arguments for the relation.
+  Basically, any relation only accepts a few number of entity types and this could be an important constraint
+   for inducing relations. Relations of each cluster should have similar selectional preferences and
+    accept same entity types. Type-LDA is proposed for this reason, it will induce entity types 
+    and relation clusters jointly to benefit more from selectional preferences of relations.
 
@@
 
-\section{Summaru}
+\section{Summary}
 \label{ch:conclusion}

### 2013-07-19 term-paper/paper.tex
Added: paper.pdf

@@
 
-   	In the second model, \textbf{Rel1-LDA},The only difference is that  more features are used in the learning procedure.
+   	In the second model, \textbf{Rel-LDA1},The only difference is that  more features are used in the learning procedure.
    	 The idea is that using more features could be useful as tie-breakers and also discriminators between instances
@@
    	     \item Named entity pair: The type of source and destination named entity.
+   	     \item Syntactic pair: The type of dependency edges connecting source and destination to the head.
    	   \end{itemize}
@@
 
+    The generative model is modified in a way that features of arguments (source and destination)
+    will be generated from two new distributions, $T_1$ \& $T_2$ which are modeling entity types. The graphical model
+    is shown in fig ???. This model not only clusters relations but also clusters entities to entity clusters.
+
+    For their experiments on all three models they have set the number of relation clusters to 100 and for Type-LDA they used 
+     50 entity clusters. Choosing other numbers of relation clusters in the range of 50 to 200 is shown to be not very significant.
+
 \subsection {Evaluation}
 \label{ch:evaluation}
+
+Yao et al. have evaluated their models in different settings. Their comparison against Mintz et al.?? previous work
+ will be mentioned in the next chapter which is dedicated to distant supervision. They have used human judgments 
+ to measure their models precision. Humans are asked to label 50 instances in each relation cluster and in order to measure
+ the recall, induced relations are compared against Freebase. Table ?? shows the results.
+
+ ???
+
+ Like most of the other models, antonymy is not handled in their model and therefor for example they have
+ \emph{X was born in Y} and \emph{X die in Y} in one cluster.
+
+ Entity clusters also sometimes suffer from high-frequency or low-frequency words and for example, `New York`
+ , is in the same cluster as other publications like `New York Times`, `Vanity Fair` and \ldots
+
+ Yao et al. have shown that they have induced relations in different granularity from Freebase and reported some relations
+ which are not mentioned in Freebase but positively hold. For example, Freebase relation \emph{worksFor}
+  is subsumed with more relations each indicates a different role of employment relation. \emph{leaderOf}
+   and \emph{editorOf} are such examples. This will boost the idea of inducing heirarchical 
+   relations which will be discussed more in the last chapter.
 

### 2013-07-20 term-paper/paper.tex
Added: USP

@@
 
-\section{PATTY}
-\label{ch:unsupervised}
+In this section we will review the first unsupervised semantic parsing method which proposed by Poon and Domingos ???,
+we will first define what is semantic parsing and after describing the method in ??? we show its application for relation extraction.
+In the evaluation subsection we will compare this model to its related models and analyze its advantages and disadvantages.
+
+\subsection{Semantic Parsing}
+\label{ch:definition}
+
+Semantic parsing is mapping a sentence to its formal meaning represntation ???%cite{PoonDomingos2009}
+The aim is to represent a natural language text with first-order logic. One can derive a semantic parse of a sentence
+by starting from a lexicon of atomic formulas and combining each fragment to build a composition of 
+formulas combined with quantifiers and logical connectives. In ???%cite{PoonDomingos2009} 
+ the lexicon will be induced from a raw corpus. It is in contrast to traditional means of semantic parsing with manually
+  produced lexicons.
+
+  The main challange in unsupervised semantic parsing is that for a single semantic representation there could be
+  several syntactic realizations or even harder, different surface representations. For example, all of the
+   sentences below has a same semantic representation:
+   \begin{itemize}
+     \item Microsoft buys Skype
+     \item Microsoft acquires the VoIP company Skype
+     \item Skype is acquired by Microsoft Corporation
+     \item The Redmond software giant buys Skype
+     \item Microsoft’s purchase of Skype,\ldots
+   \end{itemize}
+
+   A simple lexicon to represent all of the examples above is:
+
+   $$ BUY(n_1)$$
+   $$ \lambda x_2.BUYER(n_1 , x_2) \; \;  \lambda x_3.BOUGHT(n_1 , x_3) $$
+   $$ MICROSOFT(n_2) \; \; SKYPE(n_3)$$
+
+   Having a corpus of sentences in natural language, USP %???\cite{domingosPoon}
+    will induce such a lexicon and will also extract a formal representation for each sentence. In the next 
+    subsection we will review the necessary steps toward this goal.
+\subsection{Model Description}
+\label{ch:model}
+
+\subsection {Evaluation}
+\label{ch:evaluation}
+sdgdsg
 

### 2013-07-21 term-paper/paper.tex
Modified: USP model desc

@@
 \label{ch:model}
+In this section we will first identify the three key ideas that the model is built upon them and then 
+we will describe the necessary steps toward unsupervised semanitc parsing.
+
+Three observations are made by the authors which is crucial to understand the model assumptions:
+
+\begin{enumerate}
+  \item Different syntactic variations of predicates and constants can be clustered together to express
+   a same meaning. This can be learned from a raw corpus, in contrast to supervised methods which use meaning annotation of text.
+   \item Not only fixed elements in a relation can be clustered together but also arbitrary forms with same sub-forms to co-occured forms 
+   can be put in a cluster. In this way the meaning compisiton will be learned through clustering of the forms.
+   \item Learning syntax and semantics jointly is a complex problem. Authors have shown that translating a syntactic analyses
+   to semantic parse has superior performance over joint learning of syntax and semantics. In this way, a model can be built on the shoulder
+   of state-of-the-art syntactic parsers.
+
+\end{enumerate}
+
+Based on these assumptions, they propose a method to model joint probabibility of the dependency tree
+and its meaning representation. Markov Logic Networks (MLN) ??? is used to represent the meaning of a sentence.
+For each sentence we will have an undirected graphical model (Markov network) which each nodes corresponds to atoms
+and cliques correspond to first-order clauses. The best meaning representation is the one which 
+maximizes the probability of the observed dependency. %???cite{Titov}
+These are the major steps of the USP system:
+\begin{description}
+  \item[Dependency Parsing] \hfill \\
+  the authors believe that dependency parsing is a better starting point that phrase-structure parsing, since it expresses
+   the relation-argument structure at the lexical level. They have used Minipar ??? to make the results more comparable with previous
+   methods, e.g. DIRT.
+  \item[Converting Dependency Trees into Quasi-Logical Forms] \hfill \\
+  Extracting lambda forms and atoms (lexical entries) is done by a deterministic procedure. 
+  Arguments of a dependency path will be converted to atoms, their predicate consists of the lemma and their part-of-speech tags.
+  Each edge from the head to arguments will be a predicate labeled as type of the dependency path.
+  This predicate together with two lambda function for each argument form a QLF. In this QLF, only one constant can be presented.
+
+  \item[Clustering Lambda-Forms] \hfill \\
+  It starts from atom levels and cluster them based on their relation, then it recursively clusters larger formula
+  based on their subformula lambda forms. The composition of meaning of any formula can be obtained by applying
+  \emph{lambda reduction} and substituting constants with lambda variables. At the end we will have a clustering
+  of lambda forms which each cluster contains a set of semantically equivalent lambda forms. this solves
+   the problem of having different syntactic realizations with a same meaning.
+
+  \item[Creating a Markov Logic Network] \hfill \\
+  Each atom can be modeled as a node and each first-order clause can be modeled as a feature. This is still not a complete Markov Logical
+  Network since this model needs a weighting for features.Thus, the weight of feature is defined as a weight of
+  its corredpandant clause. A log-linear distibution $$ P(x) = \frac{1}{Z}\exp{\Sigma_i{(w_i n_i (x))}} $$is used to model the probability of each clique (configuration of nodes and features).
+
+  \item[Learning the weights of MLN] \hfill \\
+  \item[Finding the Best Semantic Parse] \hfill \\
+  A semantic parse is a partition of atoms of a QLF, assignment of its head and argument form to a cluster. 
+  This can be seen as a structre prediction problem. Given the described MLN and its paramters, inference can
+   be done by finding a Maximum A Posterior solution. An exact solution needs a summing over all possible syntactic realizations and
+   possible dependency parses, therefor a greedy algorithm to search for a good solution is proposed 
+   by the authors.   
+\end{description}
 

### 2013-07-21 term-paper/paper.tex
Modified: USP evaluation

@@
   Network since this model needs a weighting for features.Thus, the weight of feature is defined as a weight of
-  its corredpandant clause. A log-linear distibution $$ P(x) = \frac{1}{Z}\exp{\Sigma_i{(w_i n_i (x))}} $$is used to model the probability of each clique (configuration of nodes and features).
+  its corredpandant clause. A log-linear distibution 
+  $$ P(x) = \frac{1}{Z}\exp{\Sigma_i{(w_i n_i (x))}} $$
+  is used to model the probability of each clique (configuration of nodes and features).
+  $Z$ is a normalization factor which its computation is infeasible. $w_i$ is the weight of $i$th formula.
+  $n_i$ is number of satisfied atoms and formulas that appeared in the sentence.
 
   \item[Learning the weights of MLN] \hfill \\
+  Given the dependency parse and QLF forms, weights can be learned from data such as the log-likelihood
+  of having QLFs given the dependency trees will be maximized. The form of likelihood is:
+  $$ L_{\theta}(QLF) = \log{\Sigma_L{P_\theta{(QLF, L)}}}$$ where $L$ is a semantic parse.
+
+  Since the summation of all possible semantic parses is infeasible, a set of additional constraints on the form
+  of clauses and also a prior over weights are added to model to make the learning feasible. Their algorithm
+  merges any possible two clusters to form a bigger cluster or create a new cluster if either increases the likelihood.
   \item[Finding the Best Semantic Parse] \hfill \\
@@
 \label{ch:evaluation}
-sdgdsg
+Since USP is the first system for unsupervised semantic parsing, it is compared against other models in a Question/Answering task.
+GENIA is an Q/A annotated dataset in medical domain and USP has been shown to find the answers with 88\% precision
+which is about 10\% higher than TextRunner and more than 30\% better than DIRT. It is worthwhile to mention that
+GENIA is a rather small dataset.
+
+There are two major problems observed by the authors themselves and others for USP.
+\begin{itemize}
+ \item Same as the other models that we have already seen,
+ it doesn't address the separation of antonym relations
+ \item It is mentioned in ??? %\cite{Yao} \cite{Titov}
+ that USP suffers from using a large memory and therefore low ability to scale to bigger dataset. 
+ \end{itemize}
+ Two modifications for USP runtime is proposed in ???%\cite{Deep USP} \cite{Titov}.
+  In ???  %\cite{Titov}
+  it is proposed to use directed graphical models instead of undirected graphs(MLN) to increase the learning and inference speed.
+  The result is slighty worse than the original model but it performs faster than USP.
+  In ???%\cite{Deep USP} 
+  a new representation of the model is given in the framwork of deep learning which yields 
+  the same performance but with faster learning algorithm.
+
+  In the next section we will see another model which shows improvement to DIRT, TextRunner and USP 
+  and is much more scalable than the former.
 

### 2013-07-21 term-paper/paper.tex
Added: DIRT

@@
 \usepackage{amsmath}
+\usepackage{framed, color}
+\usepackage{fancybox}
+\definecolor{shadecolor}{rgb}{0.8,0.8,0.8}
+
 %\usepackage{natbib}
@@
 \label{ch:unsupervised}
+
+Lin and Pantel in ??? proposed an unsupervised method for finding paraphrases from text which  
+proved to be very influential and their method, \textbf{DIRT}, has become a classic work. In addition
+ to this paper we will also review two major improvements to DIRT proposed by Pantel et al. ???.
+DIRT tries to cluster semantically equivalent relations based on the similarity of their arguments. Relations
+(or inference rules) that DIRT can discover are mostly limited to paraphrases which are a subset of possible types of inference rules.
+
+In this section, first, the key idea of DIRT will be elaborated more and then we will review the algorithm and analyze the observations.
+Based on these observations, two other methods, ISP and LEDIR ???, which try to address a subset of DIRT's problems, will be discussed.
+
+\subsection{Extended Distributional Hypothesis}
+\label{ch:assumption}
+
+Synonymy of words and other semantic relations in word level have been studied very well in literature.
+For example Pereira et al. in ??? %\cite{Distributional Clustering of English Words}
+cluster similar words which convey a similar meaning. The key assumption in this work and related ones is so called
+ \textbf{Distributional Hypothesis} ??? %\cite{Harris}
+ .It tells that words which usually occur in similar context have similar meaning. This idea can be generalized
+  to phrases or predicates-arguments. A set of relations or phrases that appear in a similar context
+  are semantically equivalent. Lin and Pantel have extended this idea with giving a slightly different notion
+   of context. The context that they define in their work is the dependency path between a predicate of
+    relation and its arguments. As the Extended Distributional Hypothesis states:
+    \begin{shaded}
+     If two paths tend to occur in similar contexts, the meaning of the path tend to be similar 
+    \end{shaded}
+
+    In this sense, the task of finding paraphrases or semantically equivalent relations
+     can be formulated as \emph{finding paths with similar meaning}. 
+     An algorithm to find such a similar path is a topic of the next aprt.
+
+\subsection{Model Description}
+\label{ch:model} 
+DIRT starts with dependency parsing of sentences and continues with pruning of these dependency trees.
+It amounts to several conditions on dependency path such as that only nouns will be kept as arguments. 
+Additionally, all the function words will be filtered to have the dependecy relations that only connect
+two content words. Dependency relations with less than a certain number of occurence will be removed to make the task feasible.
+After the pruning phase, a set of binary relations with a list of nouns associated to each of their slots is generated. 
+The similarity of relations can be expressed based on similarity of associated list of slot words. Lin and Pantel
+have used \emph{pointwise mutual information (pmi)} two measure similarity of slots. 
+It measures the independency of two random variables or the amount of
+information they containt for each other. The similarity function for relations  is a geometric average
+of similarity of correspondent slots.
+
+Instead of clustering of relations which seems to be a natural next phase,
+ they maintain a databases of triples (relation and its slots).For each relation queried
+  they measure the similarity of relations which share at least one common slot word and then report top-40 of them.
+
+\subsection{Evaluation and Analysis}
+\label{ch:model}
+
+  Based on what Lin and Pantel have reported in ??? they extracted 231,000 unique paths from a newspaper corpus.
+  They have used a manually geenrated paraphrases to evaluate their method. For six questions from TREC-8 ???
+  they have generated top-40 paraphrases and then evaluate them manually to report percentage of correctly found paraphrases.
+  This approach has a very obvious flaw which is that number of returned paraphrases is fixed. Clustering has this 
+  advantage that each cluster of relations can have arbitrary number of paraphrases.
+  Average accuracy for these six questions is 50.3\% and no paraphrases have been found for one of the questions.
+  The recall can't be measured easily since many correctly found paraphrases by DIRT are not discovered by humans.
+
+  Beside the problem of having fixed number of returned paraphrases, there are three other major 
+  problems after observing the results of DIRT which two of them will be addressed by Pantel et al. and
+  will be discussed in the next parts. These problems are:
+
+  \begin{enumerate}
+    \item Antonymy of relations can not be captured with DIRT and antonym relations will be returned as similar relations. After more than
+    a decade, it is still an open problem
+    \item DIRT results are very noisy in a sense that it doesn't induce the type of arguments.
+    \item DIRT results or paraphreses are always considered as bi-directional. Relation \emph{A} implies relation \emph{B} and vice versa.
+    This assumption doesn't hold for many instances and needs to be regarded in the model.
+  \end{enumerate}
+
+In the next two sections ISP and LEDIR methods will be covered as proposed improvements to DIRT to filter erroneous relations.
+
+\subsection{Inference Selectional Preferences}
+\label{ch:model}
+
+Selectional preference of a predicate is the constraint that it puts over the class of words can be used as its arguments.
+For example: \emph{x drives y} has a selectional preference on the second argument for motorized 
+vehicles with more than two wheels and \emph {x rides y}
+has a preference for vehicles or animals which rider is positioned astride. %\cite{ThesisMechura}
+
+In order to model this type of constraint on discovery of paraphrases, Pantel et al. have proposed that
+relations which are similar but are not sharing a same class of arguments should be filtered out. For each relation, 
+they compute a distribution of possible semantic classes for its arguments. For two equivalent relations, they will be kept
+if this distribution is similar for both.
 
@@
   relations. Relations and entities belong to a hierarchy of types and therefore the constraints they put on each other
-  should be learnt as well.
+  should be learned as well.
   %\citep{Yao2011}\citep{Alfonesca2012}\citep{NakasholeWeikum2012}
@@
   \item[Relations and entities are sharing information within each other.] \hfill \\
-  Relations and entities should be learnt jointly since they share same explanatory factors (hidden variables)
-  . Meaning of a entity can be learnt from its relation to other entities and same argument holds among relations.
+  Relations and entities should be learned jointly since they share same explanatory factors (hidden variables)
+  . Meaning of a entity can be learned from its relation to other entities and same argument holds among relations.
   Basically, the model should be able to carry multi-task learning. 

### 2013-07-21 term-paper/paper.tex
Added: pictures DIRT finished

@@
 \usepackage{fancybox}
+\usepackage{graphicx}
 \definecolor{shadecolor}{rgb}{0.8,0.8,0.8}
@@
 for relation extraction task is provided which identifies important aspects and
-difficulties of the task. In the second chapter, five major previous works are
-briefly reviewed. The third chapter is dedicated to a weakly supervised method, distant supervision, which is 
-necessary due to its impact on recent advances in the task. And
+difficulties of the task. In the second chapter, four major previous works are
+briefly reviewed. And
 finally in the last chapter, the paper will be concluded by comparison of discussed methods and important lessons learned from each of them.
@@
 \subsection{Inference Selectional Preferences}
-\label{ch:model}
+\label{ch:improve}
 
@@
 they compute a distribution of possible semantic classes for its arguments. For two equivalent relations, they will be kept
-if this distribution is similar for both.
+if this distribution is similar for both.Yao et al. ??? also incorporate selectional preferences to their model and which we
+will see in detailed in the last section.
+
+Two models are proposed to compute this distribution. The first one, the distribution is computed jointly for both of arguments
+and the second one two different distributions are computed for each argument. The computation is just a simple count.
+
+The question that naturally arises is that how one can obtain these semantic classes? The answer is that
+they are obtainable from lexical resources such as WordNet or they can be induced by clustering words.
+The authors have used both methods. As the first approach, they have used top level nodes in WordNet and all their successors together
+as semantic classes. They have also used CBC clustering algorithm ??? to induce semantic classes. 
+In ??? brown and ??? Lin WU a similar approach but with different clustering algorithms has been chosen 
+and the later is the current state-of-the-art method.
+
+After computing selectional preferences for each relation, those relations which don't have similar selectional preference
+distribution will be considered as inequivalent. The plausibility of an inference rule which contains two relations is
+discussed in detailed in ??? %cite{LEDIR}.
+
+Inducing word clusters and using independent selectional preferences distributions has been shown to outperform other models
+and have the highest increase of accuracy compare to DIRT.
+
+\subsection{Direction of Inference Rules}
+\label{ch:improve}
+So far all the similar relations are considered to be paraphrases nad they have bi-directional semantic equivallency relation.
+
+Since this assumption doesn't hold for all the inference rules that are discovered by DIRT, Pantel et al. pushed their model
+another step further to find the direction of implications among relations, in addition to just find equivalent relations.
+
+They have used the results from DIRT and ISP to find out which direction holds for an implication over two relations.
+having $relation_i \iff relation_j$ they want to examine if it holds or either of $relation_i \implies relation_j$
+or $relation_j \implies relation_i$ is the correct rule.
+
+the key assumption in ??? is that the direction is most likely from a specific relation to a more general relation.
+By specific relation they mean a relation that has a narrow set of semantic classes and selectional preferences and 
+a general relation is a relation with broader semantic classes. Number of acceptable semantic classes for each relation is a 
+good measure for such purpose. If this number is greater for the antecedent then the direction is right otherwise it should be flipped.
+
+In the next section we will review a method which operates in web-scale and extract relations with bootstraping.
 
@@
     please read ?? and ??.
-    Rel-LDA is decribed with a graphical model in figure ???.
+    Rel-LDA is decribed with a graphical model 
+     \begin{figure}[h!]
+  \caption{Rel-LDA}
+  \centering
+    \includegraphics[width=0.5\textwidth]{rel-lda.eps}
+    \label{fig:rel-lda}
+\end{figure} in Figure ~\ref{fig:rel-lda} .
+
     Shaded circles are showing the observable variables and other circles are hidden variables except 
@@
     will be generated from two new distributions, $T_1$ \& $T_2$ which are modeling entity types. The graphical model
-    is shown in fig ???. This model not only clusters relations but also clusters entities to entity clusters.
+    is shown in
+     \begin{figure}[h!]
+  \caption{Type-LDA}
+  \centering
+    \includegraphics[width=0.5\textwidth]{type-lda.eps}
+    \label{fig:type-lda}
+\end{figure} 
+Figure ~\ref{fig:type-lda} .
+    This model not only clusters relations but also clusters entities to entity clusters.
 
@@
 
-Yao et al. have evaluated their models in different settings. Their comparison against Mintz et al.?? previous work
- will be mentioned in the next chapter which is dedicated to distant supervision. They have used human judgments 
+\iffalse Yao et al. have evaluated their models in different settings.  Their comparison against Mintz et al.?? previous work
+ will be mentioned in the next chapter which is dedicated to distant supervision. \fi They have used human judgments 
  to measure their models precision. Humans are asked to label 50 instances in each relation cluster and in order to measure
@@
 
+\iffalse
 \chapter{Weakly Supervised on Relation Extraction Task}
@@
 with their own conclusion and future work.
+\fi
 

### 2013-07-22 term-paper/paper.tex
modified: Bibliography

@@
 Unsupervised Relation Extraction. In the first chapter, the definition and a general background
-for relation extraction task is provided which identifies important aspects and
-difficulties of the task. In the second chapter, four major previous works are
+for relation extraction task is provided. In the second chapter, four major previous works are
 briefly reviewed. And
-finally in the last chapter, the paper will be concluded by comparison of discussed methods and important lessons learned from each of them.
+finally in the last chapter, the paper will be concluded by identifying important aspects and
+difficulties of the task and important lessons learned from each of the discussed relation extraction systems.
 
@@
 
+\iffalse
 This part provides an overall introduction of the unsupervised relation extraction task, including
 definition and various formulations of the task.
+\fi
 
-\section{Definition}
-\label{ch:intro}
+Nowadays searching through Internet is the first step we take if we want to get answer to our question.
+We convert our questions to sequences of keywords and search engines are trying 
+to lead us to webpages where might contain the answer to our questions, they return us a set of related
+documents which are sorted by their popularity and similarity of their text to our query.
+In this way, users themselves are responsible to find the desired knowledge 
+from documents. The next generation search engines should go further than current 
+approaches in understanding the meaning of a query and the underlying semantics of documents on 
+the web. The next natural improvement is to return a piece of information which directly approaches to 
+answer the user question. For this reason, the elements of a query, concepts or entities and 
+their relations should be identified and documents ( which might have the answer) should be mapped to the 
+same space of entities and relations in order to find the the desired information in the question.
 
-Relation Extraction is the task of detecting and classifying semantic rela-
-tionship between named entities (NE). The goal of this task is to find a triple
+Relation Extraction is the task of detecting and classifying semantic relationship 
+between named entities (NE). The goal of this task is to find a triple
 of binary relations and their arguments. For instance, we want to induce a
 relation like \emph{bornIn} with its arguments which could be for example like this:\emph{ (
-bornIn, Richard Stallman, New York )}. Applications of such task is numerous
+bornIn, Beata Nyari, Budapest )}. Applications of such task is numerous
 in natural language processing; Question/Answering, machine translation and
@@
 
-From a classic method, DIRT, to very famous frameworks ,
-TextRunner or distant supervision, and more recent works e.g. PATTY,
+From a classic method, DIRT \cite{Lin2001}, to very famous frameworks ,
+TextRunner\cite{Bankoa} or distant supervision\cite{Mintz2009}, and more recent works e.g. PATTY\cite{Nakashole2012a},
 all are examples of several different family of approaches. These methods could
@@
 interpretation and (4) underlying family of methods they use.
-he content of your proposal. Each topic occupies one section, each
-with their own conclusion and future work.
-In this section we will review these major works. We will discuss their formulation of the task, their models
+In this section we will review four major works on unsupervised relation discovery.
+ We will discuss their formulation of the task, their models
  and the features they incorporate, the model constraints and finally we will take a look at how good a model is performing.
@@
 
-Lin and Pantel in ??? proposed an unsupervised method for finding paraphrases from text which  
-proved to be very influential and their method, \textbf{DIRT}, has become a classic work. In addition
- to this paper we will also review two major improvements to DIRT proposed by Pantel et al. ???.
+Lin and Pantel in \cite{Lin2001} proposed an unsupervised method for finding paraphrases from text which  
+proved to be very influential and their method, \textbf{DIRT}, has become a classic work in literature.
+ In addition
+ to this paper we will also review two major improvements to DIRT proposed in \cite{Bhagat2007} and \cite{Pantel2007}.
 DIRT tries to cluster semantically equivalent relations based on the similarity of their arguments. Relations
@@
 In this section, first, the key idea of DIRT will be elaborated more and then we will review the algorithm and analyze the observations.
-Based on these observations, two other methods, ISP and LEDIR ???, which try to address a subset of DIRT's problems, will be discussed.
+Based on these observations, two other methods, ISP \cite{Pantel2007} and LEDIR \cite{Bhagat2007}, 
+which try to address a subset of DIRT's problems, will be discussed.
 
@@
 Synonymy of words and other semantic relations in word level have been studied very well in literature.
-For example Pereira et al. in ??? %\cite{Distributional Clustering of English Words}
+For example Pereira et al. in \cite{Pereira1993} 
 cluster similar words which convey a similar meaning. The key assumption in this work and related ones is so called
- \textbf{Distributional Hypothesis} ??? %\cite{Harris}
- .It tells that words which usually occur in similar context have similar meaning. This idea can be generalized
+ \textbf{Distributional Hypothesis} \cite{Harris1981}
+ . It tells that words which usually occur in similar context have similar meaning. This idea can be generalized
   to phrases or predicates-arguments. A set of relations or phrases that appear in a similar context
@@
 
-  Based on what Lin and Pantel have reported in ??? they extracted 231,000 unique paths from a newspaper corpus.
-  They have used a manually geenrated paraphrases to evaluate their method. For six questions from TREC-8 ???
+  Based on what Lin and Pantel have reported in \cite{Lin2001} they extracted 231,000 unique paths from a newspaper corpus.
+  They have used a manually geenrated paraphrases to evaluate their method. For six questions from TREC-8 
   they have generated top-40 paraphrases and then evaluate them manually to report percentage of correctly found paraphrases.
@@
 vehicles with more than two wheels and \emph {x rides y}
-has a preference for vehicles or animals which rider is positioned astride. %\cite{ThesisMechura}
+has a preference for vehicles or animals which rider is positioned astride \cite{Mechura2008} .
 
-In order to model this type of constraint on discovery of paraphrases, Pantel et al. have proposed that
+In order to model this type of constraint on discovery of paraphrases, Pantel et al. \cite{Pantel2007} have proposed that
 relations which are similar but are not sharing a same class of arguments should be filtered out. For each relation, 
 they compute a distribution of possible semantic classes for its arguments. For two equivalent relations, they will be kept
-if this distribution is similar for both.Yao et al. ??? also incorporate selectional preferences to their model and which we
+if this distribution is similar for both.Yao et al. \cite{Yao2011} also incorporate selectional preferences to their model and which we
 will see in detailed in the last section.
@@
 The authors have used both methods. As the first approach, they have used top level nodes in WordNet and all their successors together
-as semantic classes. They have also used CBC clustering algorithm ??? to induce semantic classes. 
-In ??? brown and ??? Lin WU a similar approach but with different clustering algorithms has been chosen 
+as semantic classes. They have also used CBC clustering algorithm \cite{Pantel2002} to induce semantic classes. 
+In \cite{Brown1992} and \cite{Lin2009} a similar approach but with different clustering algorithms has been chosen 
 and the later is the current state-of-the-art method.
@@
 distribution will be considered as inequivalent. The plausibility of an inference rule which contains two relations is
-discussed in detailed in ??? %cite{LEDIR}.
+discussed in detailed in \cite{Bhagat2007} and \cite{Kotlerman2010} .
 
@@
 
-the key assumption in ??? is that the direction is most likely from a specific relation to a more general relation.
+the key assumption in \cite{Bhagat2007} is that the direction is most likely from a specific relation to a more general relation.
 By specific relation they mean a relation that has a narrow set of semantic classes and selectional preferences and 
@@
 
-In this section we will review the first unsupervised semantic parsing method which proposed by Poon and Domingos ???,
-we will first define what is semantic parsing and after describing the method in ??? we show its application for relation extraction.
+In this section we will review the first unsupervised semantic parsing method which proposed by Poon and Domingos \cite{Poon2009},
+we will first define what is semantic parsing and after describing the method in \cite{Poon2009} we show its application for relation extraction.
 In the evaluation subsection we will compare this model to its related models and analyze its advantages and disadvantages.
@@
 
-Semantic parsing is mapping a sentence to its formal meaning represntation ???%cite{PoonDomingos2009}
+Semantic parsing is mapping a sentence to its formal meaning represntation \cite{Poon2009}
 The aim is to represent a natural language text with first-order logic. One can derive a semantic parse of a sentence
 by starting from a lexicon of atomic formulas and combining each fragment to build a composition of 
-formulas combined with quantifiers and logical connectives. In ???%cite{PoonDomingos2009} 
+formulas combined with quantifiers and logical connectives. In \cite{Poon2009} 
 the lexicon will be induced from a raw corpus. It is in contrast to traditional means of semantic parsing with manually
@@
 
-   Having a corpus of sentences in natural language, USP %???\cite{domingosPoon}
+   Having a corpus of sentences in natural language, USP \cite{Poon2009}
     will induce such a lexicon and will also extract a formal representation for each sentence. In the next 

### 2013-07-22 term-paper/paper.tex
Modified: Bibliography

@@
 \subsection{Model Description}
-\label{ch:model} 
+\label{ch:dirt-model} 
 DIRT starts with dependency parsing of sentences and continues with pruning of these dependency trees.
@@
 \subsection{Inference Selectional Preferences}
-\label{ch:improve}
+\label{ch:sel-pref}
 
@@
 Based on these assumptions, they propose a method to model joint probabibility of the dependency tree
-and its meaning representation. Markov Logic Networks (MLN) ??? is used to represent the meaning of a sentence.
+and its meaning representation. Markov Logic Networks (MLN) \cite{Richardson2006} is used to represent the meaning of a sentence.
 For each sentence we will have an undirected graphical model (Markov network) which each nodes corresponds to atoms
 and cliques correspond to first-order clauses. The best meaning representation is the one which 
-maximizes the probability of the observed dependency. %???cite{Titov}
+maximizes the probability of the observed dependency \cite{Titov2011}.
 These are the major steps of the USP system:
@@
   the authors believe that dependency parsing is a better starting point that phrase-structure parsing, since it expresses
-   the relation-argument structure at the lexical level. They have used Minipar ??? to make the results more comparable with previous
+   the relation-argument structure at the lexical level. They have used Minipar \cite{Lin2002} to make the results more comparable with previous
    methods, e.g. DIRT.
@@
  it doesn't address the separation of antonym relations
- \item It is mentioned in ??? %\cite{Yao} \cite{Titov}
+ \item It is mentioned in \cite{Yao2011} and \cite{Titov2011}
   that USP suffers from using a large memory and therefore low ability to scale to bigger dataset. 
  \end{itemize}
- Two modifications for USP runtime is proposed in ???%\cite{Deep USP} \cite{Titov}.
-  In ???  %\cite{Titov}
+ Two modifications for USP runtime is proposed in \cite{Poon2013} and \cite{Titov2011}.
+  In \cite{Titov2011}
    it is proposed to use directed graphical models instead of undirected graphs(MLN) to increase the learning and inference speed.
   The result is slighty worse than the original model but it performs faster than USP.
-  In ???%\cite{Deep USP} 
+  In \cite{Poon2013} 
   a new representation of the model is given in the framwork of deep learning which yields 
@@
 
-In this section we will review the method proposed for relation discovery  by Yao et. al. 
+In this section we will review the method proposed for relation discovery  by Yao et. al. \cite{Riedel2013}  
 The method they  proposed is an unsupervised method using generative models which is based on 
@@
 \item Sentence split
-\item POS tagging (?? all last three steps with Stanford tools)
-\item Named entity tagging ( ?? Finkel2005)
-\item Dependency parsing (??MaltParser)
+\item POS tagging %(?? all last three steps with Stanford tools)
+\item Named entity tagging % ( ?? Finkel2005)
+\item Dependency parsing %(??MaltParser)
 \end{enumerate}
@@
  path most likely as a verb which relates two mentioned named entities. These types of 
- paths are collected and based on some conditions that we have already discussed in (??? DIRT), non-important links are filtered out.
-
- As an example ???
+ paths are collected and based on some conditions that we have already discussed in Section ~\ref{ch:dirt-model} ,
+  non-important links are filtered out.
  Finally in this phase, 2.5 million dependency paths were collected 
@@
 All the three models in this work are generative models. Generative models are jointly modeling hidden variables and observable variables and 
-are in contrast to discriminative models. For more information on generative models please see ?? and ??.\\
+are in contrast to discriminative models. For more information on generative models please see \cite{Murphy2012}.\\
 
-\textbf{Rel-LDA} is the first model proposed in (?? Yao). 
+\textbf{Rel-LDA} is the first model proposed in \cite{Riedel2013}. 
 In this model, features, $f$, are generated from a distribution , $\Phi_{rf}$. Each type
@@
    chosen for this purpose in the paper. For more on the role of priors and specially Dirichlet prior
-    please read ?? and ??.
+    please read \cite{Teh2007} and \cite{Gershman2012} .
     Rel-LDA is decribed with a graphical model 
@@
     and relation clusters jointly to benefit more from selectional preferences of relations. 
+    As we have already mentioned in Section ~\ref{ch:sel-pref},
+     this idea have been used in \cite{Pantel2007} .
 
@@
  to measure their models precision. Humans are asked to label 50 instances in each relation cluster and in order to measure
- the recall, induced relations are compared against Freebase. Table ?? shows the results.
-
- ???
+ the recall, induced relations are compared against Freebase.
 
@@
    and \emph{editorOf} are such examples. This will boost the idea of inducing heirarchical 
-   relations which will be discussed more in the last chapter.
+   relations which will be discussed more in the last chapter. A similar approach which tries to induce
+    hierarchical structures is \cite{Alfonseca2012} .
 
@@
    and is also supported in the literature.
-   %\citep{Yates2007}\citep{Mintz2009}
+   \cite{Mintz2009} \cite{Yates2007}
 
@@
   Relation extraction task is definitely more than finding paraphrases. The model should be able to handle
-  long-distance relations among entities as well as hidden semantic indications of a relation.
-
-  %\citep{PoonDomingos2009}
+  long-distance relations among entities as well as hidden semantic indications of a relation. \cite{Poon2009}
 
@@
   relations. Relations and entities belong to a hierarchy of types and therefore the constraints they put on each other
-  should be learned as well.
-  %\citep{Yao2011}\citep{Alfonesca2012}\citep{NakasholeWeikum2012}
+  should be learned as well.\cite{Yao2011} \cite{Alfonseca2012} \cite{Nakashole2012a}
 
@@
   from such resources strongly contributes to convergance of any model to a better 
-  objective configurations.
-  %\citep{Mintz2009}\citep{Bordes2011}\citep{Yao2011}
+  objective configurations.\cite{Yao2011} \cite{Mintz2009}
 
@@
   . Meaning of a entity can be learned from its relation to other entities and same argument holds among relations.
-  Basically, the model should be able to carry multi-task learning. 
-  %\citep{Yao2011}\citep{Bordes2011}
+  Basically, the model should be able to carry multi-task learning. \cite{Yao2011}
 
@@
 
-Provide an overview of what you have done and what need to be done.
+In this paper, we reviewd four influential works on \textbf{Unsupervised Relation Extraction}:
+\begin{enumerate}
+  \item DIRT
+  \item TextRunner
+  \item USP
+  \item Rel-LDA \& Type-LDA
+\end{enumerate}
+
+We described each model and analyzed the strength and weakness of them. We also showed some improvements over these
+ methods in literature. At the end, we highlighted main aspects of the task that each model tried to address a subset of them.
 

### 2013-07-22 term-paper/paper.tex
Sent to Pinkal

@@
 We convert our questions to sequences of keywords and search engines are trying 
-to lead us to webpages where might contain the answer to our questions, they return us a set of related
+to lead us to web pages where might contain the answer to our questions, they return us a set of related
 documents which are sorted by their popularity and similarity of their text to our query.
@@
 between named entities (NE). The goal of this task is to find a triple
-of binary relations and their arguments. For instance, we want to induce a
+of binary relations and their arguments \cite{Androutsopoulos2009}. For instance, we want to induce a
 relation like \emph{bornIn} with its arguments which could be for example like this:\emph{ (
@@
 in natural language processing; Question/Answering, machine translation and
-text summarization are systems that benefit from relation extraction.
+text summarization are systems that benefit from relation extraction \cite{Androutsopoulos2009}.
 
@@
      can be formulated as \emph{finding paths with similar meaning}. 
-     An algorithm to find such a similar path is a topic of the next aprt.
+     An algorithm to find such a similar path is a topic of the next part.
 
@@
 It amounts to several conditions on dependency path such as that only nouns will be kept as arguments. 
-Additionally, all the function words will be filtered to have the dependecy relations that only connect
-two content words. Dependency relations with less than a certain number of occurence will be removed to make the task feasible.
+Additionally, all the function words will be filtered to have the dependency relations that only connect
+two content words. Dependency relations with less than a certain number of occurrence will be removed to make the task feasible.
 After the pruning phase, a set of binary relations with a list of nouns associated to each of their slots is generated. 
@@
 It measures the independency of two random variables or the amount of
-information they containt for each other. The similarity function for relations  is a geometric average
+information they contain for each other. The similarity function for relations  is a geometric average
 of similarity of correspondent slots.
@@
   Based on what Lin and Pantel have reported in \cite{Lin2001} they extracted 231,000 unique paths from a newspaper corpus.
-  They have used a manually geenrated paraphrases to evaluate their method. For six questions from TREC-8 
+  They have used a manually generated paraphrases to evaluate their method. For six questions from TREC-8 
   they have generated top-40 paraphrases and then evaluate them manually to report percentage of correctly found paraphrases.
@@
     \item DIRT results are very noisy in a sense that it doesn't induce the type of arguments.
-    \item DIRT results or paraphreses are always considered as bi-directional. Relation \emph{A} implies relation \emph{B} and vice versa.
+    \item DIRT results or paraphrases are always considered as bi-directional. Relation \emph{A} implies relation \emph{B} and vice versa.
     This assumption doesn't hold for many instances and needs to be regarded in the model.
@@
 After computing selectional preferences for each relation, those relations which don't have similar selectional preference
-distribution will be considered as inequivalent. The plausibility of an inference rule which contains two relations is
+distribution will be considered as nonequivalent. The plausibility of an inference rule which contains two relations is
 discussed in detailed in \cite{Bhagat2007} and \cite{Kotlerman2010} .
@@
 \label{ch:improve}
-So far all the similar relations are considered to be paraphrases nad they have bi-directional semantic equivallency relation.
+So far all the similar relations are considered to be paraphrases and they have bi-directional semantic equivalency relation.
 
@@
 good measure for such purpose. If this number is greater for the antecedent then the direction is right otherwise it should be flipped.
+A similar approach has been used in \cite{Kotlerman2010} which additionally confirm the results of this work.
 
-In the next section we will review a method which operates in web-scale and extract relations with bootstraping.
+In the next section we will review a method which operates in web-scale and extract relations with bootstrapping.
 
@@
 \label{ch:unsupervised}
+
+TextRunner is the first system that addresses open domain relation extraction in web-scale \cite{Yates2007}. In this section
+ we will describe the architecture of TextRunner and then we will review two main elements of this system, \emph{Learner} and
+  \emph{Extractor}, in more details and shortly we will comment on the third element \emph{Assessor}.
+
+\subsection{TextRunner Architecture}
+\label{ch:arch}
+
+Original TextRunner paper proposed four elements for its architecture:
+\begin{itemize}
+  \item Learner
+  \item Extractor
+  \item Assessor
+  \item Query Processor
+\end{itemize}
+
+The last sub-system has no major role in relation extraction so we put our focus on the first three elements.
+
+\subsection{Model Description}
+\label{ch:model}
+
+TextRunner avoids using parsing for large-scale and inhomogeneous corpus like web. \emph{Learner} sub-system is responsible
+ for providing a substitution or an approximation for syntactic parsing which, called as extractor by the authors.
+  The approach that they follow in \cite{Yates2007}
+  is that they use a small corpus to train a  relation classifier and this classifer will be applied to a much bigger web corpus.
+   After parsing the small corpus, authors have used a set of predefined heuristics just based on POS tags and syntactic role 
+   of words to generate positive ad negative relation examples. The heuristics were designed as prototypes of syntactic behavior
+   of general relations and they are not dependent on any certain type of relation. 
+   For example:   $E_1 \;\; Verb \;\; E_2$ as template of \emph{X created Y} or 
+   $ E_1 \; \; NP \;  Prep \; \; E_2$ for \emph{X is birthplace of Y} are such heuristics.\\
+
+    A Naive Bayes classifier is self-trained on this small dataset, it 
+   starts with small seed of relations for training then it labels more instances in the corpus. This classifier will be used as
+    \emph{Extractor}
+   in the next phase. This classifier is not relying on any lexical or relation-specific features, hence it can operate 
+   in open domain like web \cite{Banko2009}. In the extraction phase, a maximum-entropy classifer was used to find entities and then by 
+   using the extractor learned from the previous phase, they recognize explicit relations among named entities.
+
+   These extracted relations and named entities contain many redundant or equivalent relations. The role of \emph{Assessor}
+    is to find equivalent relations. It starts with normalization of relations and entities and then based on string-similarity
+     and shared relational attributes it finds explicitly equivalent relations, it should be mentioned that 
+     this approach differs from DIRT which finds semantically equivalent relations.
+
+\subsection{Evaluation}
+\label{ch:eval}
+
+     TextRunner is evaluated against a manually tagged dataset of 500 sentences. While the precision is in 
+      the accepted level, 86.6\%, recall is low (23.2\%). The recall has been improved by using a \emph{Conditional Random Field}
+       \cite{Banko2009} as classifier instead of Naive Bayes. Precision slightly is improved by using a CRF for about 2\%
+        but we see a tremendous increase in recall which levels to 45.2\% .
+
+TextRunner suffers from using very shallow features. Its ability to find relations is limited to explicitly mentioned
+ relations and it can only find them if they occur in a sentence. In the next part we will review a model 
+ which does not suffer from these disadvantages due to its deeper semantic analysis.
 
@@
 
-Semantic parsing is mapping a sentence to its formal meaning represntation \cite{Poon2009}
+Semantic parsing is mapping a sentence to its formal meaning representation \cite{Poon2009}
 The aim is to represent a natural language text with first-order logic. One can derive a semantic parse of a sentence
@@
 
-  The main challange in unsupervised semantic parsing is that for a single semantic representation there could be
+  The main challenge in unsupervised semantic parsing is that for a single semantic representation there could be
   several syntactic realizations or even harder, different surface representations. For example, all of the
@@
 In this section we will first identify the three key ideas that the model is built upon them and then 
-we will describe the necessary steps toward unsupervised semanitc parsing.
+we will describe the necessary steps toward unsupervised semantic parsing.
 
@@
    a same meaning. This can be learned from a raw corpus, in contrast to supervised methods which use meaning annotation of text.
-   \item Not only fixed elements in a relation can be clustered together but also arbitrary forms with same sub-forms to co-occured forms 
-   can be put in a cluster. In this way the meaning compisiton will be learned through clustering of the forms.
-   \item Learning syntax and semantics jointly is a complex problem. Authors have shown that translating a syntactic analyses
+   \item Not only fixed elements in a relation can be clustered together but also arbitrary forms with same sub-forms to co-occurred forms 
+   can be put in a cluster. In this way the meaning composition will be learned through clustering of the forms.
+   \item Learning syntax and semantics jointly is a complex problem. Authors have shown that translating a syntactic analysis
    to semantic parse has superior performance over joint learning of syntax and semantics. In this way, a model can be built on the shoulder
@@
 
-Based on these assumptions, they propose a method to model joint probabibility of the dependency tree
+Based on these assumptions, they propose a method to model joint probability of the dependency tree
 and its meaning representation. Markov Logic Networks (MLN) \cite{Richardson2006} is used to represent the meaning of a sentence.
@@
   Network since this model needs a weighting for features.Thus, the weight of feature is defined as a weight of
-  its corredpandant clause. A log-linear distibution 
+  its correspondent clause. A log-linear distribution 
   $$ P(x) = \frac{1}{Z}\exp{\Sigma_i{(w_i n_i (x))}} $$
@@
   A semantic parse is a partition of atoms of a QLF, assignment of its head and argument form to a cluster. 
-  This can be seen as a structre prediction problem. Given the described MLN and its paramters, inference can
+  This can be seen as a structure prediction problem. Given the described MLN and its parameters, inference can
    be done by finding a Maximum A Posterior solution. An exact solution needs a summing over all possible syntactic realizations and
@@
    it is proposed to use directed graphical models instead of undirected graphs(MLN) to increase the learning and inference speed.
-  The result is slighty worse than the original model but it performs faster than USP.
+  The result is slightly worse than the original model but it performs faster than USP.
   In \cite{Poon2013} 
-  a new representation of the model is given in the framwork of deep learning which yields 
+  a new representation of the model is given in the framework of deep learning which yields 
   the same performance but with faster learning algorithm.
@@
 abnormal style of writing like obituary content are filtered out.
-They have done several pre-processing steps:
+They have done several preprocessing steps:
 \begin{enumerate}
@@
     please read \cite{Teh2007} and \cite{Gershman2012} .
-    Rel-LDA is decribed with a graphical model 
+    Rel-LDA is described with a graphical model 
      \begin{figure}[h!]
@@
    	     \item Trigger: Any word in a dependency path except than stop words. 
-   	     \item Part of speech sequence: The sequence of pos tags of a dependency path. 
+   	     \item Part of speech sequence: The sequence of POS tags of a dependency path. 
    	     \item Named entity pair: The type of source and destination named entity.
@@
  to measure their models precision. Humans are asked to label 50 instances in each relation cluster and in order to measure
- the recall, induced relations are compared against Freebase.
+ the recall, induced relations are compared against Freebase. Rel-LDA1 and Type-LDA which are using selectional preferences features
+  are performing better than Rel-LDA. Rel-LDA1 is shown to have the best precision among other models. 
+  Rel-LDA and Type-LDA have been also compared against
+  USP and have been shown to have superior performance both in scalability and F-measure.
 
@@
   is subsumed with more relations each indicates a different role of employment relation. \emph{leaderOf}
-   and \emph{editorOf} are such examples. This will boost the idea of inducing heirarchical 
+   and \emph{editorOf} are such examples. This will boost the idea of inducing hierarchical 
    relations which will be discussed more in the last chapter. A similar approach which tries to induce
@@
   Knowledge Bases e.g. Freebase. At the same time, it is statistically shown that a supervision
-  from such resources strongly contributes to convergance of any model to a better 
+  from such resources strongly contributes to convergence of any model to a better 
   objective configurations.\cite{Yao2011} \cite{Mintz2009}
@@
   . Meaning of a entity can be learned from its relation to other entities and same argument holds among relations.
-  Basically, the model should be able to carry multi-task learning. \cite{Yao2011}
+  Basically, the model should be able to carry out multi-task learning. \cite{Yao2011}
 
@@
 
-In this paper, we reviewd four influential works on \textbf{Unsupervised Relation Extraction}:
+In this paper, we reviewed four influential works on \textbf{Unsupervised Relation Extraction}:
 \begin{enumerate}

### 2013-07-22 term-paper/paper.tex
some grammar correcting

@@
       the accepted level, 86.6\%, recall is low (23.2\%). The recall has been improved by using a \emph{Conditional Random Field}
-       \cite{Banko2009} as classifier instead of Naive Bayes. Precision slightly is improved by using a CRF for about 2\%
+       \cite{Banko2009} as classifier instead of Naive Bayes. The model precision is slightly improved by using a CRF for about 2\%
         but we see a tremendous increase in recall which levels to 45.2\% .
@@
   Relations and entities should be learned jointly since they share same explanatory factors (hidden variables)
-  . Meaning of a entity can be learned from its relation to other entities and same argument holds among relations.
+  . Meaning of an entity can be learned from its relation to other entities and same argument holds among relations.
   Basically, the model should be able to carry out multi-task learning. \cite{Yao2011}
